Modeling the Graphotactics of Low-Resource Languages Using Sequential GANs

### 2022-05-11 Paper/paper.tex
fixed mistakes

      To perform this hallucination, they aligned the lemma with its inflected form, extracted the stem, and generated new artificial examples by replacing this stem with randomly generated strings (in the language's alphabet) of equal length.\footnote{The alignment process assumes that the lemma and inflected form share a common substring.} Though a seemingly haphazard method of data augmentation, this approach allowed for an additional 10\% accuracy, on average, when tested against versions of the model that only used cross-lingual transfer.

@@

    \subsection{GANs for Data Augmentation}
      Although GANs are most popularly used for domain transfer, the same basic architecture is also a good candidate for a data augmentation strategy called hallucination in which new (fake) training examples based on a small number of existing (real) examples.

@@

  \section{Method}
    \subsection{Data Pipeline}
      All language data used was sourced from the SIGMORPHON 2019 repository and was initially formatted according the the Unimorph schema. The data for each language was gathered from their respective Wikipedia. Only the ``train-low'' sets were used for training. These datasets has only 100 examples, with each containing a lemma (base form), an inflected form, and a list of the morphological categories associated with the inflected form.\footnote{Although the ``train-low'' sets do occasionally have 1000 examples, those corresponding to the languages used in this experiment have only 100.}

@@

      On average Levenshtein distance calculations follow a similar pattern to that of model accuracy; however, this metric occasionally favors the models trained on trigram augmented data (Fig. \ref{fig:lev}). Additionally, in the case of North Frisian, a particularly difficult language to inflect (based on the accuracy results), the model trained on just the 100 original examples had a slightly lower average Levenshtein distnace.

@@

    \section*{Code and Data}
    \subsection*{Written}
    \subsection*{Referenced}
    \begin{enumerate}
      \item Code from Anastasopoulos and Neubig, 2019: \url{https://github.com/antonisa/inflection}
      \item Stem alignment code from Mans Hulden: \url{https://github.com/mhulden/crpalign}
      \item GAN training routine from Géron: \url{https://github.com/ageron/handson-ml2/blob/master/17_autoencoders_and_gans.ipynb}
      \item Data for the SIGMORPHON 2019 shared task: \url{https://github.com/sigmorphon/2019}
      \item Wasserstein loss implementation: \url{https://machinelearningmastery.com/how-to-implement-wasserstein-loss-for-generative-adversarial-networks}
    \end{enumerate}
  \bibliography{sources}
\end{document}

>>>>

      To perform this hallucination, they aligned the lemma with its inflected form, extracted the stem, and generated new artificial examples by replacing this stem with randomly generated strings (in the language's alphabet) of equal length.\footnote{The alignment process assumes that the lemma and inflected form share a common substring.} Though this random substitution may seem haphazard, the approach allowed for an additional 10\% accuracy, on average, when tested against versions of the model that only used cross-lingual transfer.

@@

    \subsection{GANs for Data Augmentation}
      Although GANs are most popularly used for domain transfer, the same basic architecture is also a good candidate for a data augmentation strategy called hallucination in which new (fake) training examples are created based on a small number of existing (real) examples.

@@

  \section{Method}
    \subsection{Data Pipeline}
      All language data used was sourced from the SIGMORPHON 2019 repository and was initially formatted according the the Unimorph schema. The data for each language was gathered from their respective Wikipedia. Only the ``train-low'' sets were used for training. These datasets have only 100 examples, and each example contains a lemma (base form), an inflected form, and a list of the morphological categories associated with the inflected form.\footnote{Although the ``train-low'' sets do occasionally have 1000 examples, those corresponding to the languages used in this experiment have only 100.}

@@

      On average Levenshtein distance calculations follow a similar pattern to that of model accuracy; however, this metric occasionally favors the models trained on trigram augmented data (Fig. \ref{fig:lev}). Additionally, in the case of North Frisian, a particularly difficult language to inflect (based on the accuracy results), the model trained on just the 100 original examples had a slightly lower average Levenshtein distance.

@@

    \section*{Code and Data}
    \subsection*{Written}
      All code can be found in this Github repo: \url{https://github.com/isaacwasserman/ml-final-project}.\\
      \\Here are some files of particular importance:
      \begin{enumerate}
        \item GAN training notebook: \url{https://github.com/isaacwasserman/ml-final-project/blob/main/word_gan/word_gan.ipynb}
        \item Augmentation script: \url{https://github.com/isaacwasserman/ml-final-project/blob/main/word_gan/augment_smart.py}
        \item Augmented datasets: \url{https://github.com/isaacwasserman/ml-final-project/tree/main/inflection/augmented_data}
      \end{enumerate}
    \subsection*{Referenced}
      \begin{enumerate}
        \item Code from Anastasopoulos and Neubig, 2019: \url{https://github.com/antonisa/inflection}
        \item Stem alignment code from Mans Hulden: \url{https://github.com/mhulden/crpalign}
        \item GAN training routine from Géron: \url{https://github.com/ageron/handson-ml2/blob/master/17_autoencoders_and_gans.ipynb}
        \item Data for the SIGMORPHON 2019 shared task: \url{https://github.com/sigmorphon/2019}
        \item Wasserstein loss implementation: \url{https://machinelearningmastery.com/how-to-implement-wasserstein-loss-for-generative-adversarial-networks}
      \end{enumerate}
  \bibliography{sources}
\end{document}
